TODO: A Survey of StarCraft AI Techniques

### 2013-02-25 survey.tex
Add Gabriel's thesis ref in the SC complexity part.
Added an abstract

{\color{blue}
\begin{abstract}
TODO: Idea of the paper is: ``one-stop guide on what is the
state of the art in StarCraft AI''. It should help people participating in the competition focus
their efforts, and also should help people implementing AI for RTS games in
general (e.g. industry).  In Gabriel's words ``RTS AI problems, Solutions, State-of-the-art, conclude on what's "solved" since \cite{Buro03rts} and what's not.''

For example, if someone wants to implement a bot, and wonders "how should I do scouting", our paper should provide a summary of the existing techniques, and pointers to know more.
\end{abstract}
}

@@

\section{Introduction}\label{sec:intro}
\IEEEPARstart{S}{ince} Michael Buro's call for research in RTS games \cite{Buro03rts}, many researchers have answered the call. Specially, AI competitions like the ``AIIDE StarCraft AI Competition'' have caused many AI techniques to be
applied to RTS AI. We will list and classify these approaches, explain their 
power and their downsides and conclude on what is left to achieve human-level 
RTS AI.

Many  challenging AI  problems can  be found  in  dynamic environments
where  one does  not have  a  perfect, complete  information of  their
current  state, as well  as their  evolution.  Road  traffic, finance,
weather  forecasts are  examples of  huge, complex,  real-life dynamic
environments. RTS games can be seen as a simplification of a real-life
environment, where there  exist simpler rules in a  finite and smaller
world, but are complex enough  to bring very difficult and interesting
problems  to  the scientific  community,  like  decision making  under
uncertainty  or  real-time  planning.   Finding  efficient  techniques
tackling  these problems  on  RTS  games can  thus  profit broader  AI
domains, but  have also concrete  and direct applications in  the huge
industry of  video games,  generating worldwide two  and a  half times
more revenue than the Film industry in 2011.

This paper, aiming to provide a one-stop guide on what is the state of
the art in StarCraft AI, is organized as follow: Section~\ref{sec:rts}
introduces real-time strategy games, in particular the game StarCraft,
and  the main  AI challenges  in RTS  games.  Section~\ref{sec:review}
reviews  the existing  work on  RTS games  tackling  these challenges.
Section~\ref{sec:bot} shows  the current state  of the art  AI players
for  StarCraft, presenting  seven AI  players participating  to annual
StarCraft    AI    competitions     for    a    couple    of    years.
Section~\ref{sec:competition}  presents these two  annual competitions
held  at the AIIDE  and CIG  conferences.  Section~\ref{sec:questions}
compiles open questions  in RTS game AI which must  be tackled to make
bots reaching a high human-level play.
% skip "empirical evidence..." for the moment
Finally, the paper concludes on discussions and perspectives.

@@

Another way to measure the complexity of the game, is by looking at the branching factor, $b$ and the depth of the game, $d$. In Chess, $b \approx 35$ and $d \approx 80$. In more complex games, like Go, $b \approx 30 - 300$, and $d \approx 150 - 200$. In StarCraft, humans can issue only one action at a time (this is because of the GUI used by the game, computer players can issue several actions, to different units, at any given time), thus, assuming a player controls between 50 to 200 units, and that each unit can execute between 4 to 20 actions (moving in each of the 4 cardinal directions, attacking units in range, use special abilities, etc.), we obtain a branching factor $b \approx  200 - 4000$. Good players can execute about 300 actions per minute, and the typical length of a game is about 25 minutes. Thus, $d \approx 7500$.

@@

\section{Empirical Evidence of What is Missing in Existing Bots}\label{sec:experiments}

{\color{blue}
Here, whatever experiments we want to include to support which aspects of RTS Game AI require more work.
}

@@

\section*{Acknowledgments} {\color{blue} This research is partially funded by projects ... and ... . The authors would like to thank Florian Richoux, author of the AIUR bot, for his helpful comments and help in early drafts of this paper. }

>>>>

\begin{abstract}
This paper presents an overview of the existing work on creating AI for real-time strategy (RTS) games. Specifically, we focus on the work performed around the game {\em StarCraft}, which has emerged in the past few years as the unified test-bed for this line of research. We describe the specific AI challenges posed by RTS games, and overview the solutions that have been explored to address them. Additionally, we also present a summary of the results of the recent StarCraft AI competitions, describing some of the architectures used by the participants. Finally, we conclude with a discussion emphasizing which problems in the context of RTS game AI have been solved, and which remain open.
\end{abstract}

@@

\section{Introduction}\label{sec:intro}
\IEEEPARstart{S}{ince} Michael Buro's call for research in real-time strategy (RTS) games \cite{Buro03rts}, many researchers have answered the call. Specially, AI competitions like the ``AIIDE StarCraft AI Competition'' have caused many AI techniques to be
applied to RTS AI. We will list and classify these approaches, explain their 
power and their downsides and conclude on what is left to achieve human-level 
RTS AI.

Many  challenging AI  problems can  be found  in  dynamic environments
where  one does  not have  a  perfect, complete  information of  their
current  state, as well  as their  evolution.  Road  traffic, finance,
weather  forecasts are  examples of  huge, complex,  real-life dynamic
environments. RTS games can be seen as a simplification of a real-life
environment, where there  exist simpler rules in a  finite and smaller
world, but are complex enough  to bring very difficult and interesting
problems  to  the scientific  community,  like  decision making  under
uncertainty  or  real-time adversarial planning.   Finding  efficient  techniques
tackling  these problems  on  RTS  games can  thus  profit broader  AI
domains, but  have also concrete  and direct applications in  the huge
industry of  video games,  generating worldwide two  and a  half times
more revenue than the Film industry in 2011.

This paper, aiming to provide a one-stop guide on what is the state of
the art in RTS AI, and with a particular emphasis on the work done in StarCraft, is organized as follows: Section~\ref{sec:rts}
introduces real-time strategy games, in particular the game StarCraft,
and  the main  AI challenges  in RTS  games.  Section~\ref{sec:review}
reviews  the existing  work on  RTS games  tackling  these challenges.
Section~\ref{sec:bot} shows  the current state  of the art  AI players
for  StarCraft, presenting  seven AI  players participating  to annual
StarCraft    AI    competitions     for    a    couple    of    years.
Section~\ref{sec:competition}  presents these two  annual competitions
held  at the AIIDE  and CIG  conferences.  Section~\ref{sec:questions}
compiles open questions  in RTS game AI which must  be tackled to make
bots reaching a high human-level play.
% skip "empirical evidence..." for the moment
Finally, the paper concludes on discussions and perspectives.

@@

Another way  to measure the complexity  of the game, is  by looking at
the branching factor, $b$ and the depth of the game, $d$, as proposed in~\cite{Gaby}. In Chess, $b \approx 35$ and $d \approx 80$. In more complex games, like Go, $b \approx 30 - 300$, and $d \approx 150 - 200$. In StarCraft, humans can issue only one action at a time (this is because of the GUI used by the game, computer players can issue several actions, to different units, at any given time), thus, assuming a player controls between 50 to 200 units, and that each unit can execute between 4 to 20 actions (moving in each of the 4 cardinal directions, attacking units in range, use special abilities, etc.), we obtain a branching factor $b \approx 200 - 4000$. Good players can execute about 300 actions per minute, and the typical length of a game is about 25 minutes. Thus, $d \approx 7500$.

@@

%\section{Empirical Evidence of What is Missing in Existing Bots}\label{sec:experiments}
%
%{\color{blue}
%Here, whatever experiments we want to include to support which aspects of RTS Game AI require more work.
%}

@@

%\section*{Acknowledgments} {\color{blue} This research is partially funded by projects ... and ... . }
